Numerical analysis of the linear vertical shear instability in astrophysical disks

### 2014-12-23 linear_adia.tex
minor updates

\subsection{Adiabatic perturbations}\label{analytic_adia}
We now extend the above discussion to general $\gamma$, but in the
adiabatic limit ($t_c\to\infty$). We eliminate variables from 
Eq. \ref{lin_mass}---\ref{lin_energy} in favor of $\delta v_z$ 
and $\Delta \equiv \nabla\cdot\delta\bm{v}$ to obtain
\begin{align}
  &\Delta\left(1 + \frac{\gamma c_s^2 k_x^2}{D}\right) = \frac{d\delta
    v_z}{dz} + \frac{\ii k_x^2}{D}\left(\ii c_s^2 \frac{d\ln\rho}{dz}
    - \frac{r}{k_x}\frac{d\Omega^2}{dz}\right)\delta v_z,\label{adia_iso1}\\
  & -\frac{\sigma^2}{c_s^2}\delta v_z = \gamma \frac{d\Delta}{dz} +
  \frac{d}{dz}\left(\frac{d\ln\rho}{dz}\delta v_z\right) +
  \left(\gamma-1\right)\frac{d\ln\rho}{dz} \Delta.\label{adia_iso2}
\end{align}
%{\bf note: incompressible mode, set delta to zero. only works for
% constant gravity.}

>>>>

\subsection{Adiabatic perturbations}\label{analytic_adia}
We now consider general $\gamma$ in the
adiabatic limit ($t_c\to\infty$). This is the opposite regime to
isothermal perturbations. We eliminate variables from 
Eq. \ref{lin_mass}---\ref{lin_energy} in favor of $\delta v_z$ 
and $\Delta \equiv \nabla\cdot\delta\bm{v}$ to obtain
\begin{align}
  &\Delta\left(1 + \frac{\gamma c_s^2 k_x^2}{D}\right) = \frac{d\delta
    v_z}{dz} + \frac{\ii k_x^2}{D}\left(\ii c_s^2 \frac{d\ln\rho}{dz}
    - \frac{r}{k_x}\frac{d\Omega^2}{dz}\right)\delta v_z,\label{adia_iso1}\\
  & -\frac{\sigma^2}{c_s^2}\delta v_z = \gamma \frac{d\Delta}{dz} +
  \frac{d}{dz}\left(\frac{d\ln\rho}{dz}\delta v_z\right) +
  \left(\gamma-1\right)\frac{d\ln\rho}{dz} \Delta.\label{adia_iso2}
\end{align}
%{\bf note: incompressible mode, set delta to zero. only works for
% constant gravity.}
